Topological Equivariant Artist Model

### 2021-12-29 slides/main.tex
sheaves breakdown

\usetheme{ccnycrest}

@@

\title{Topological Equivariant Artist Model}

\begin{frame}
	\titlepage
    Hannah Aizenman, Tom Caswell, Michael Grossberg\\
    %Committee: Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo\\
    %External Member: Dr. Marcus Hanwell
\end{frame}

@@

\begin{frame}{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

@@

\begin{frame}{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

@@

\begin{frame}{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}(MayaVi\cite{RamachandranMayaVI2011})$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}

\subsection{Algebraic Topology & Category Theory}

@@

\begin{frame}{Presheaf: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&, column sep=small]
        {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\\& \&\\
        \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] \& {} \arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf] \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
        \end{tikzcd}
\end{equation*}
\end{frame}

@@

\end{frame}
\begin{frame}{Stalk \& Germ}

\adjustbox{scale=1}{
    \begin{description}
    \item[Stalk] $\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc})$
    \item[Germ] $\dsectionc(\dbasepointc) \in \sheafc(\dbasec)$
\end{description}
}
\end{frame}

>>>>

%\usetheme{ccnycrest}

@@

\title{Topological Equivariant Artist Model}
\begin{comment}
\begin{frame}
	\titlepage
    Hannah Aizenman, Tom Caswell, Michael Grossberg\\
    %Committee: Dr. Robert Haralick, Dr. Lev Manovich, Dr. Huy Vo\\
    %External Member: Dr. Marcus Hanwell
\end{frame}

@@

%% maybe pull out the middle for now? move the 3 stages down to construction? 
\begin{frame}{What do visualization libraries do?}
    \begin{figure}
        \begin{overprint}
            \onslide<1|handout:1>\includegraphics[width=\linewidth]{figures/flow/s2.png}
            \onslide<2|handout:2>\includegraphics[width=\linewidth]{figures/flow/s_vc.png}
            \onslide<3|handout:3>\includegraphics[width=\linewidth]{figures/flow/s_mark.png}
            \onslide<4|handout:4>\includegraphics[width=\linewidth]{figures/flow/s3.png}
        \end{overprint}
    \end{figure}
\end{frame}

@@

%flip columns
\begin{frame}{Frameworks for Expressing Visual Equivariance}
    \begin{description}
        \item[linguistically] visualization has syntax, semantics, grammar expresses how to design structure preserving visualizations
        \cite{mackinlayAutomatingDesignGraphical1986,mackinlayAUTOMATICDESIGNGRAPHICAL1987,wilkinsonGrammarGraphics2005}

@@

\begin{frame}{General purpose libraries generally can't\cite{toryRethinkingVisualizationHighlevel2004}}
    \begin{figure}
        \includegraphics[height=.3\textheight]{../paper/figures/k_different_types.png}
    \end{figure}
    \begin{enumerate}
        \item Matplotlib\cite{hunterMatplotlib2DGraphics2007} $\rightarrow$Seaborn\cite{waskom2020seaborn}, xarray \cite{hoyer2017xarray} 
        \item D3 \cite{bostockDataDrivenDocuments2011}
        \item VTK \cite{hanwellVisualizationToolkitVTK2015,geveciVTK2012}(MayaVi\cite{RamachandranMayaVI2011})$\rightarrow$ Titan\cite{brianwylieUnifiedToolkitInformation2009}, ParaView\cite{ahrens2005paraview}
    \end{enumerate}
\end{frame}
\end{comment}
\subsection{Algebraic Topology & Category Theory}

@@

\begin{frame}{Subsets?}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Subsets?}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}  \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf]  \& {}  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] \& {}  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] \& {}  \arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}

    \begin{description}
        \item<2-|handout:2->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<3-|handout:3>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@
